---
title: "Checks on sampled component of IPE data"
author: "Anthony Twesigye"
date: "28/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

# read packages
library(tidyverse)
library(lubridate)
library(glue)
library(leaflet)

# read data 
df_tool_data <- readxl::read_excel("../inputs/Individual_Profiling_Exercise_Questionnaire_for_Sampled_Households.xlsx") %>% 
  mutate(i.check.uuid = `_uuid`,
         i.check.start_date = as_date(start),
         i.check.settlement = settlement,
         start = as_datetime(start),
         end = as_datetime(end))

# log
df_log <- readxl::read_excel("../inputs/combined_checks_IPE_questionnaire_for_sampled_households.xlsx")

# tool
df_survey <- readxl::read_excel("../inputs/Individual_Profiling_Exercise_Tool.xlsx", sheet = "survey")
df_choices <- readxl::read_excel("../inputs/Individual_Profiling_Exercise_Tool.xlsx", sheet = "choices")

# average survey time

average_survey_time <- df_tool_data %>% 
  mutate(int.survey_time_interval = lubridate::time_length(end - start, unit = "min"),
         int.survey_time_interval = ceiling(int.survey_time_interval)
         )%>% 
  select(int.survey_time_interval) %>% 
  summarise(average_time = mean(int.survey_time_interval, na.rm = TRUE))


# number of surveys that have comment "oprion already exists"
n_surveys_option_exists <- df_log %>% 
  filter(str_detect(string = comment, pattern = fixed('already exist', ignore_case = TRUE))) %>% 
  group_by(uuid) %>% 
  select(uuid) %>% 
  unique() %>% 
  nrow()

# more than 5 instances of "oprion already exists"
n_surveys_option_exists_instances <- df_log %>% 
  filter(!type %in% c("add_option"), str_detect(string = comment, pattern = fixed('already exist', ignore_case = TRUE))) %>% 
  group_by(uuid) %>% 
  summarise(number_of_occurances = n()) %>% 
  filter(number_of_occurances > 1) %>% 
  nrow()
  

```


## General observation: The data looks good

>Total checked surveys **`r nrow(df_tool_data)`**

>The average time of surveys: **`r round(average_survey_time, 0)`** min

>Surveys with other_specify when given options already exist : **`r n_surveys_option_exists`** out of the total surveys **`r nrow(df_tool_data)`**

>Surveys with more than one instance of other_specify when given options already exist : **`r n_surveys_option_exists_instances`** out of the total surveys **`r nrow(df_tool_data)`**

## most appearing questions in the checking log

```{r}

# most appearing questions
df_log %>% 
  filter(!is.na(name),  !type %in% c("add_option")) %>% 
  # left_join(df_survey_modified, by = "name") %>% 
  group_by(name, label) %>% 
  summarise(number_of_occurances = n()) %>% 
  filter(number_of_occurances > 5) %>% 
  arrange(desc(number_of_occurances))
  
```

