---
title: "Checks on sampled component of IPE data"
author: "Anthony Twesigye"
date: "28/01/2022"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

# read packages
library(tidyverse)
library(lubridate)
library(glue)
library(leaflet)

# read data 
df_tool_data <- readxl::read_excel("../inputs/Individual_Profiling_Exercise_Questionnaire_for_Sampled_Households.xlsx") %>% 
  mutate(i.check.uuid = `_uuid`,
         i.check.start_date = as_date(start),
         i.check.settlement = settlement,
         start = as_datetime(start),
         end = as_datetime(end))

# log
df_log <- readxl::read_excel("../inputs/combined_checks_IPE_questionnaire_for_sampled_households.xlsx")

# tool
df_survey <- readxl::read_excel("../inputs/Individual_Profiling_Exercise_Tool.xlsx", sheet = "survey")
df_choices <- readxl::read_excel("../inputs/Individual_Profiling_Exercise_Tool.xlsx", sheet = "choices")

# average survey time

average_survey_time <- df_tool_data %>% 
  mutate(int.survey_time_interval = lubridate::time_length(end - start, unit = "min"),
         int.survey_time_interval = ceiling(int.survey_time_interval)
         )%>% 
  select(int.survey_time_interval) %>% 
  summarise(average_time = mean(int.survey_time_interval, na.rm = TRUE))


# number of surveys that have comment "oprion already exists"
n_surveys_option_exists <- df_log %>% 
  filter(str_detect(string = comment, pattern = fixed('already exist', ignore_case = TRUE))) %>% 
  group_by(uuid) %>% 
  select(uuid) %>% 
  unique() %>% 
  nrow()

# more than 5 instances of "oprion already exists"
n_surveys_option_exists_instances <- df_log %>% 
  filter(!type %in% c("add_option"), str_detect(string = comment, pattern = fixed('already exist', ignore_case = TRUE))) %>% 
  group_by(uuid) %>% 
  summarise(number_of_occurances = n()) %>% 
  filter(number_of_occurances > 1) %>% 
  nrow()
  
dt_with_modified_options <- function(x){
  DT::datatable(x,
                rownames = FALSE,
                options = list(
                  columnDefs = list(list(targets = list(1,2))),
                  pageLength = 20,
                  initComplete = JS(
                    "function(settings, json) {",
                    "$(this.api().table().header()).css({'background-color': '#333', 'color': '#fff'});",
                    "}")
                )
  )
}

```


## General observation: The data looks good

>Total checked surveys **`r nrow(df_tool_data)`**

>The average time of surveys: **`r round(average_survey_time, 0)`** min

>Surveys with other_specify when given options already exist : **`r n_surveys_option_exists`** out of the total surveys **`r nrow(df_tool_data)`**

>Surveys with more than one instance of other_specify when given options already exist : **`r n_surveys_option_exists_instances`** out of the total surveys **`r nrow(df_tool_data)`**

>Surveys without gps coordinates: **`r nrow(df_log %>% dplyr::filter(issue_id %in% c("no_gps_coordinates")))`**

### Most appearing questions in the checking log

```{r, echo = FALSE}
# most appearing questions
df_log %>% 
  filter(!is.na(name), !type %in% c("add_option")) %>% 
  group_by(name, label) %>% 
  summarise(number_of_occurances = n()) %>% 
  filter(number_of_occurances > 5) %>% 
  arrange(desc(number_of_occurances)) %>% 
  dt_with_modified_options()
  
```
### Surveys with less survey time

```{r, echo = FALSE}
df_log %>% 
  filter(issue_id == "less_survey_time") %>% 
  select(uuid, issue, comment) %>% 
  dt_with_modified_options()

```

### Questions with similar text and formatting in other_specify

```{r, echo = FALSE}
df_log %>% 
  filter(!is.na(name), !type %in% c("add_option"), !issue_id %in% c("no_gps_coordinates")) %>% 
  select(uuid, name, label, other_text) %>% 
  group_by(name, label, other_text) %>% 
  summarise(number_of_occurances = n()) %>% 
  filter(number_of_occurances > 3) %>% 
  dt_with_modified_options()

```

## Some identified questions that may require restructuring or adding options or emphasising with enumerators

**2.4 Who constructed the shelter?**

This question has several responses related to "renting" or "landlord"

This could imply adding another question before this asking if they own the shelter 

**2.5.1 If Yes, ask about the type of the latrine**

There were reponses specifying **"plastic_latrine"** which is not in the current options

**reason_not_able_access_latrine/**
**2.5.4 If Yes, are there family members who are not able to access the latrine?**
There were reponses specifying **"Babies, Below age, Young children"** this can be grouped as **"young_children"**

**2.6.7 If any, what is the main kind of handwashing facility that you have access to?**

There were reponses specifying **"basin"** which is not in the current options

**3.2 What were the household's 3 most important sources of earnings during the last 12 months? **

most_important_sources_of_earnings_rank3: has several responses in the other_text as **"none"**

**7.3 Through which channels would you like receiving the information?**

There were reponses specifying **"phone_call"** which is not in the current options

**reason_un_able_access_clean_water/**
**2.8 Are there family members who are not able to access clean water?**
**2.8.1 If Yes, why**

There were reponses specifying **"Babies, Below age, Young children"** this can be grouped as **"young_children"**

**2.9.8 Do you have any electronic waste (e-waste) in your home (batteries, solar panels, solar lamps, phones, etc.?**
**2.9.10 If yes, how is it managed?**

There were reponses specifying **"dispose_in_latrine"** which is not in the current options



## Location of GPS points within the settlement

