---
title: "Summary of checks on sampled component of IPE data"
author: "REACH"
date: ""
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(dirname(inputFile), '/checks_on_sampled_component_of_IPE_data_', format(Sys.Date(), '%Y_%m_%d'),'.html')) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

# read packages
library(tidyverse)
library(lubridate)
library(glue)
library(leaflet)

source("../R/support_functions.R")

# read data 
df_tool_data <- readxl::read_excel("../inputs/Individual_Profiling_Exercise_Questionnaire_for_Sampled_Households.xlsx") %>% 
  mutate(i.check.uuid = `_uuid`,
         i.check.start_date = as_date(start),
         i.check.settlement = settlement,
         start = as_datetime(start),
         end = as_datetime(end),
         across(starts_with("calc_"), .fns = ~as.numeric(.)))

df_data_support_cl_log <- df_tool_data %>% 
  mutate(latitude = as.numeric(`_gps_coordinates_latitude`),	
         longitude = as.numeric(`_gps_coordinates_longitude`)) %>% 
  select(uuid = `_uuid`, latitude, longitude, zone, village)

# log
log_file <- "../inputs/combined_checks_IPE_questionnaire_for_sampled_households.xlsx"

df_log <- readxl::read_excel(log_file) %>% 
  filter(!adjust_log %in% c("delete_log")) %>% 
  left_join(df_data_support_cl_log, by = "uuid")

df_log_gps <- readxl::read_excel(log_file)

# tool
df_survey <- readxl::read_excel("../inputs/Individual_Profiling_Exercise_Tool.xlsx", sheet = "survey")
df_choices <- readxl::read_excel("../inputs/Individual_Profiling_Exercise_Tool.xlsx", sheet = "choices")

# settlement layer
df_settlement_layer <- readr::read_rds("../inputs/settlement_layer.rds") %>%
  # sf::st_transform(crs = 32636 ) %>%
  # sf::st_buffer(dist = 150) %>%
  sf::st_transform(crs = 4326 )

# number of surveys that have value already in choices
n_surveys_option_exists <- df_log %>% 
  filter(!is.na(value), str_detect(string = so_sm_choices, pattern = value)) %>% 
  group_by(uuid) %>% 
  select(uuid) %>% 
  unique() %>% 
  nrow()

# more than 5 instances where the choice already exists
n_surveys_option_exists_instances <- df_log %>% 
  filter(!type %in% c("add_option"), str_detect(string = so_sm_choices, pattern = value)) %>% 
  group_by(uuid) %>% 
  summarise(number_of_occurances = n()) %>% 
  filter(number_of_occurances > 5) %>% 
  nrow()

dt_with_modified_options <- function(x){
  DT::datatable(x,
                rownames = FALSE,
                options = list(
                  columnDefs = list(list(targets = list(1,2))),
                  pageLength = 20,
                  initComplete = JS(
                    "function(settings, json) {",
                    "$(this.api().table().header()).css({'background-color': '#333', 'color': '#fff'});",
                    "}")
                )
  )
}

```


### General observations

>Total checked surveys: **`r nrow(df_tool_data)`**

>The average time of surveys: **`r get_average_survey_time(df_tool_data)`** min

<!-- >Surveys with other_specify when given options already exist : **`r n_surveys_option_exists`** out of the total surveys **`r nrow(df_tool_data)`** -->

<!-- >Surveys with more than five instance of other_specify when given options already exist : **`r n_surveys_option_exists_instances`** out of the total surveys **`r nrow(df_tool_data)`** -->

>Surveys without gps coordinates: **`r nrow(df_log_gps %>% dplyr::filter(issue_id %in% c("no_gps_coordinates")))`**

### Most appearing questions in the checking log

```{r, echo = FALSE}
# most appearing questions
df_log %>% 
  filter(!is.na(name), !type %in% c("add_option")) %>% 
  group_by(name, label) %>% 
  summarise(number_of_occurances = n()) %>% 
  filter(number_of_occurances > 5) %>% 
  arrange(desc(number_of_occurances)) %>% 
  dt_with_modified_options()

```

### Some detected outliers

>**Calculated Monthly Expenditure**\
**[calc_monthly_expenditure]**\
The outliers have been detected based on the interval formed by the `2.5 and 97.5 percentiles` \
>lower limit: `r scales::number_format( scale = 1, big.mark = ",")(quantile(df_tool_data$calc_monthly_expenditure, 0.025, na.rm = TRUE))`, 
>upper limit: `r scales::number_format( scale = 1, big.mark = ",")(quantile(df_tool_data$calc_monthly_expenditure, 0.975, na.rm = TRUE))`

```{r, echo = FALSE}
df_log %>% 
  filter(issue_id == "logic_c_outlier") %>% 
  select(uuid, settlement, name, current_value, issue, comment) %>% 
  dt_with_modified_options()
```

### Surveys with less survey time

```{r, echo = FALSE}
df_log %>% 
  filter(issue_id == "less_survey_time") %>% 
  select(uuid, issue, comment) %>% 
  dt_with_modified_options()

```

### Questions with similar text and formatting in other_specify

```{r, echo = FALSE}
df_log %>% 
  filter(!is.na(name), !type %in% c("add_option"), !issue_id %in% c("no_gps_coordinates")) %>% 
  select(uuid, name, label, other_text) %>% 
  group_by(name, label, other_text) %>% 
  summarise(number_of_occurances = n()) %>% 
  filter(number_of_occurances > 3) %>% 
  dt_with_modified_options()

```

### Some identified questions that may require restructuring or adding options or emphasising with enumerators

>**2.4 Who constructed the shelter?**\
**[constructed_shelter]**\
This question has several responses related to **"renting"** or **"landlord"**\
This could imply adding another question before this asking if they own the shelter 

>**2.5.1 If Yes, ask about the type of the latrine**\
**[latrine_type]**\
There were reponses specifying **"plastic_latrine"** which is not in the current options

>**2.5.4 If Yes, are there family members who are not able to access the latrine?**\
**[reason_not_able_access_latrine]**\
There were reponses specifying **"Babies, Below age, Young children"** this can be grouped as **"young_children"**

>**2.6.7 If any, what is the main kind of handwashing facility that you have access to?**\
**[handwashing_facility]**\
There were reponses specifying **"basin"** which is not in the current options

>**3.2 What were the household's 3 most important sources of earnings during the last 12 months? **\
**[most_important_sources_of_earnings_rank_3]**\
Has several responses in the other_text as **"none"**

>**7.3 Through which channels would you like receiving the information?**\
**[channels_to_receive_information]**\
There were reponses specifying **"phone_call"** which is not in the current options

>**2.8 Are there family members who are not able to access clean water?**\
**2.8.1 If Yes, why**\ 
**[reason_un_able_access_clean_water]**\
There were reponses specifying **"Babies, Below age, Young children"** this can be grouped as **"young_children"**

>**2.9.8 Do you have any electronic waste (e-waste) in your home (batteries, solar panels, solar lamps, phones, etc.?**\
**2.9.10 If yes, how is it managed?**\ 
**[how_electronic_waste_is_managed]**\
There were reponses specifying **"dispose_in_latrine"** which is not in the current options



### Summary of GPS points outside the settlement shapefile

Table of the points

```{r, echo = FALSE, out.width="100%"}
# table
df_log %>%
  filter(issue_id %in% c("point_out_of_settlement_boundary")) %>%
  select(uuid, settlement, zone, village, issue) %>% 
  dt_with_modified_options()

```

Map of the points

```{r, echo = FALSE, out.width="100%"}
# popup
labels_pts <- ~sprintf(
  "<strong>Settlement: %s</strong><br/>
      Zone :  <strong>%s</strong><br/>
      Village :  <strong>%s</strong><br/>
      uuid :  <strong>%s</strong><br/>
      Issue :  <strong>%s</strong><br/>",
  settlement, zone, village, uuid, issue
) %>%
  lapply(htmltools::HTML)

labels_v1 <- ~sprintf(
  "<strong>District: %s</strong><br/>
      Settlement :  <strong>%s</strong>",
  District, Settlement_Name) %>% 
  lapply(htmltools::HTML)

# leaflet map
df_log_pts_out_of_boundary <- df_log %>%
  filter(issue_id %in% c("point_out_of_settlement_boundary"), !is.na(longitude), !is.na(latitude))

settlements_in_checks <- df_log_pts_out_of_boundary %>% pull(settlement) %>% unique()

df_settlements_in_checks <- df_settlement_layer %>% 
filter(Settlement_Name %in% settlements_in_checks)

leaflet() %>%
  # addTiles() %>% 
  addProviderTiles(providers$Esri.WorldGrayCanvas,
                   options = providerTileOptions(minZoom = 1.75, maxZoom = 15.5),
                   group="Esri Gray Canvas") %>%
  setView(lng = 32.2903, lat= 1.3733, zoom = 6.75) %>% 
  addMiniMap( width = 80, height = 80, position = "bottomleft", zoomAnimation = TRUE,  toggleDisplay = TRUE) %>%
  addPolygons( data = df_settlements_in_checks,
               color = "white",
               options = pathOptions(clickable = TRUE),
               fillColor = "red",
               fillOpacity = 0.3,
               weight = 1,
               opacity = 1,
               label = labels_v1,
               labelOptions = labelOptions(style = list("font-weight" = "normal"),
                                           textsize = "15px",
                                           direction = "auto", opacity =0.75),
               layerId = ~District,
               dashArray = "3",
               highlight = highlightOptions(weight = 2,
                                            color = "#666",
                                            dashArray = "",
                                            fillOpacity = 0.4,
                                            bringToFront = TRUE)
  ) %>%
  addCircleMarkers(data = df_log_pts_out_of_boundary,
                   ~longitude,
                   ~latitude,
                   popup = labels_pts,
                   radius = 8,
                   color = "red",
                   stroke = FALSE, fillOpacity = 0.9,
                   label = labels_pts,
                   clusterOptions = markerClusterOptions())
```

